### 2015-06-08 LOI/inc2.tex
minor edits.

Our overall technical approach is based on an application-aware runtime
realization of tradeoffs in data representation, data placement and data
access. We will allow users to plug-in their knowledge 
about the data, represented not as bytes but as motifs, allowing the I/O and 
storage system to understand user
intentions, the relationships between data objects, and also data access
and transport patterns. This will facilitate efficient mapping of data from
user space onto various storage tiers, and application-guided
data reductions/transformations.

@@

Incorporating awareness of the data content and user intent  into
our decision making and data management process is integral to our approach. For example, 
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those containing features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into the middleware and storage,
we will be able to selectively store data at different levels, and allow a user to select 
not only what data to retrieve but also specify an acceptable timeframe and accuracy.

@@

different portions of a single dataset, even a single variable, at different
levels of the storage hierarchy and apply different data transformation
operations to each portion. For example, full data can be queued to tape while

@@

stored in NVM or even RAM within the storage hierarchy. The storage system will
support the metadata and plug-ins required to support this data storage
approach.

@@

\textbf{Second}, new storage access APIs will be developed that understand the

@@

through knowledge of both the data quality stored in different storage

@@

tiers, can manage (with the user in the loop) the tradeoff between data precision and time to
retrieve. This storage system support will be executed and managed through our middleware, 

>>>>

Our overall technical approach is based on an application-aware runtime
realization of tradeoffs in data representation, data placement and data
access. We will allow users to plug-in their knowledge 
about the data, represented not as bytes but as motifs, allowing the I/O and 
storage system to understand user
intentions, the relationships between data objects, as well as data access
and transport patterns. This will facilitate efficient mapping of data from
user space onto various storage tiers, and application-guided
data reductions/transformations.

@@

Incorporating awareness of the data content and user intent into
storage and data management process is integral to our approach. For example, 
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those with features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve if left unmanaged. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into the middleware and storage,
we will be able to selectively store data at different levels, and allow a user to select 
not only what data to retrieve but also specify an acceptable timeframe and accuracy.

@@

different versions of a single variable to different
levels of the storage hierarchy and allow each version to be processed 
differently. For example, full data can be queued to tape while

@@

stored in non-volatile memory (NVM) or even RAM within the storage hierarchy. 
The storage system will support the metadata and plug-ins required to support
this data storage approach.

@@

\textbf{Second}, new storage access APIs will be developed that incorporates the

@@

through the knowledge of both data quality stored in different storage

@@

tiers, can manage (with the user in the loop) the tradeoff between error bound and the time to
retrieve data. This storage system support will be executed and managed through our middleware, 
